%-------------------------
% CV for Northeastern University Faculty in Latex
% Author : Zoe Kearney
% Based off of: https://www.overleaf.com/latex/templates/coles-resume-template/qhpynjcvjpcj
% Follows: https://theprofessorisin.com/2016/08/19/dr-karens-rules-of-the-academic-cv/
% License : MIT
%------------------------

% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{xcolor}
\usepackage[colorlinks=true,linkcolor=.]{hyperref}
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=1in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks
\hypersetup{%
	colorlinks=false,
	pdfborderstyle={/S/U/W 1},
	urlbordercolor=black
}

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% Begin document
\begin{document}
	
	% Disable page numbers
	\pagestyle{empty}
	
	% Header
% Header
% Header
\begin{center}
	\textbf{\Huge Parsa Niavand }\\[6pt] % Name
	Tehran, Iran \quad | \quad \href{mailto:vvsparsa@gmail.com}{Email} \quad | \quad \href{https://www.github.com/parsany}{GitHub} \quad | \quad \href{https://www.linkedin.com/in/parsany}{LinkedIn} \quad | \quad \href{https://www.parsany.ir}{parsany.ir}
\end{center}
	
	%------------------------
	% Skills
	
	\section*{SKILLS}
	
	\textbf{Programming Languages:}
	Typescript, Python, SQL, Bash
	\noindent
	\newline
	\textbf{Web Development:}
	Next.js, React, NestJS, Tailwind CSS, tRPC
	\noindent
	\newline
	\textbf{Databases \& Caching:}
	PostgreSQL, Redis, Prisma ORM, SQLite
	\noindent
	\newline
	\textbf{DevOps:}
	Docker, Linux Server, Nginx, Git, AWS S3
	\newline
	\textbf{Spoken Languages:}
	\textbf{Persian:} Native \;\; \textbf{English:} Bilingual
	

	%------------------------
	
	% Projects
	
	\section*{PROJECTS}
	
	\noindent
	\textbf{Battery ESP/MSK E-Commerce} (Production Phase) \hfill \small{\hypersetup{pdfborderstyle={/S/U/W 0}}\href{https://parsany.ir/projects/esp}{[Link]}} \vspace*{2pt} \\
	Co-developed production environments for two enterprise dual-language websites and an internal administration panel using a monorepo architecture. Implemented serial number warranty validation tools backed by NestJS and a PostgreSQL database, complete with admin user permissions controls (RBAC).\vspace{6pt} \\

	\noindent
	\textbf{Goldenbat GPS Tracking} \hfill \small{\hypersetup{pdfborderstyle={/S/U/W 0}}\href{https://app.goldengps.ir}{[Link]}} \vspace*{2pt} \\
	Co-developed an enterprise-grade GPS tracking web-application, landing and management dashboard connected directly to IoT GPS hardware endpoints. Engineered high-frequency backend ingestion endpoints to process real-time status tracking, live mapping coordinates, and historical vehicle paths and Geofencing. Developed a fully featured web administration panel using Next.js and tRPC to manage groupings, device assignments, and active user accounts.\vspace{6pt} \\

	\noindent
	\textbf{Alzahra Gold Wholesaler B2B Platform} \hfill \small{\hypersetup{pdfborderstyle={/S/U/W 0}}\href{http://app.alzahragold.com/}{[Link]}} \vspace*{2pt} \\
	Developed the high-performance B2B digital gold web portal frontend landing page using Next.js and Tailwind CSS. Contributed to the development of the client-side customer panel, implementing interactive features to streamline commercial workflows and enable institutional buyers to purchase jewelry purchases. Integrated client-side structural views alongside secure wholesale transactional layers connected to a team-implemented Django backend API. \vspace{6pt} \\
	
	\noindent
	\textbf{Atrafian Chat \& Social Ecosystem} \hfill \small{\hypersetup{pdfborderstyle={/S/U/W 0}}\href{https://atrafian.ir}{[Link]}} \vspace*{2pt} \\ 
	Solely architected and engineered an enterprise-grade real-time web application featuring a native mobile build using Turborepo and Capacitor.js. Implemented high-concurrency messaging and real-time social communication pipelines utilizing Socket.io powered by a NestJS backend ecosystem, backed by a high-efficiency Redis caching layer and secure MinIO S3 media object storage. Developed a completely separate administrative dashboard panel utilizing Next.js to isolate system operations, user management, and Role-Based Access Control (RBAC). \vspace{6pt} \\
	
	\noindent
	\textbf{Taxiland Ride-Sharing Platform} \hfill \small{\hypersetup{pdfborderstyle={/S/U/W 0}}[Archived MVP]} \vspace*{2pt} \\
	Collaborated on an intercity transportation web application and responsive driver routing system. Developed a rapid web-based administration management panel using Next.js and tRPC allowing dispatch operators to handle dynamic driver assignment and process user support tickets.\vspace{6pt} \\
	
	% Employment Section 
	\section*{RELATED EMPLOYMENT}
	\noindent
	\textbf{Fullstack Web Developer} \\
	 Organization Contract / Freelance  \\
	January 2024 - Current
	\begin{itemize}[leftmargin=*]
		\item Architected complete web applications using Next.js, React, and NestJS backends across distributed code environments.
		\item Deployed high-fidelity user layouts utilizing Tailwind CSS alongside unified backend architectures inside Turborepo monorepos.
		\item Built performant server-side configurations, custom caching layers, and high-performance type-safe API routers.
	\end{itemize}
	\noindent
	
	\vspace*{6pt}
	\noindent
	\textbf{Frontend Freelance Developer} \\
	Independent Contract \\
	June 2023 -- November 2023
	\begin{itemize}[leftmargin=*]
		\item Built and shipped responsive, client-facing website frontends using Next.js, React, and CSS.
		\item Handled on-page technical SEO, set up metadata structures, and optimized page loading speeds for local business landing pages.
		\item Converted design mockups and Figma frames into clean, interactive, and modular UI components.
	\end{itemize}

% Education Section
\section*{EDUCATION}

\noindent
\textbf{B.S. in Computer Science} \hfill SRBIAU - Tehran, Iran \\ 


	
\end{document}